RUPEE: A fast and accurate purely geometric protein structure search

### 2018-11-13 docs/rupee.tex
edits

>>>>

The length of a shingle is chosen to balance false positives, in the case of shorter shingles, against false negatives, in the case of longer shingles. 
In \cite{Ayoub2017}, we used 4 consecutive descriptors for our shingles. 
With the additions discussed in the \emph{Operating modes} section below, we have found RUPEE is more tolerant of false positives and so accordingly we have cast a wider net by decreasing the shingle length to 3.
